---
title: "Mizer Example Calibrated Food-webs"
output: html_document
---
```{r include=FALSE}
  library(mizer)
  library(mizerExamples)
```

Mizer includes a number of calibrated multi-species systems:

 * North Sea (`NS_param` from Blanchard et al, 2014; included with the mizer package). This calibration is made with a species-specific interaction matrix and gear. **Note of caution**: this calibration is done with eRepro=1.  This means that simulations overestimates reproduction severely, and the calibration should be used with caution.
 * North Sea (`NorthSea_params`), Baltic Sea (`Baltic_params`), Benguela current (`Benguela_params`), North East US Continental Shelf (`NEUSCS_params`), and the Barents Sea (`Barents_params`) (from Jacobsen et al, 2016). These systems are calibrated with purely size-based predation, i.e., no species-specific interactions. They are set up with three fishing gears targeting small, medium and large species. 

The models are available as MizerParams objects. Importing, running, and plotting is as simple as:

```{r}
  param = Barents_params
  sim = project(param)
  plot(sim)
```

The models are calibated to specific efforts on each species. For example, the Barents Sea has three fleets: small, medium, and large. Simulating with the calibrated efforts is done by:
```{r}
  sim = project(Barents_params, effort = c(small = 1.1, medium = 0.5, large = 0.75))
```

The specific efforts are described in the help pages for each calibrated model.



