---
title: "Mizer Example Calibrated Food-webs"
output: html_document
---

Mizer includes a number of calibrated multi-species systems:

 * North Sea (`NS_param` from Blanchard et al, 2014; included with the mizer package). This calibration is made with a species-specific interaction matrix and gear. **Note of caution**: this calibration is done with eRepro=1. This means that reproduction is close to the maximum reproduction `R_max` and thus the model may be less sensitive to fishing than is realistic, and the calibration should be used with caution.
 * North Sea (`NorthSea_params`), Baltic Sea (`Baltic_params`), Benguela current (`Benguela_params`), North East US Continental Shelf (`NEUSCS_params`), and the Barents Sea (`Barents_params`) (from Jacobsen et al, 2016). These systems are calibrated with purely size-based predation, i.e., no species-specific interactions. They are set up with three fishing gears targeting small, medium and large species. 

The models are available as MizerParams objects. Running, and plotting is as simple as:

```{r}
library(mizerExamples)
sim <- project(Barents_params)
plot(sim)
```

The models are calibrated to specific efforts for each of a number of fishing
gear. For example, the Barents Sea model has three gears: small, medium, and
large, and is callibrated with the efforts:
```{r}
getInitialEffort(Barents_params)
```

To see which species are caught by these gears, we look at the gear parameters
data frame:
```{r}
gear_params(Barents_params)
```

Simulating with a different effort is done by:
```{r}
  sim <- project(Barents_params, effort = c(small = 0.5, medium = 0.2, large = 0.5))
plot(sim)
```

The calibrated efforts are described in the help pages for each calibrated model.

